\documentclass[autodetect-engine,dvipdfmx-if-dvi,ja=standard,a4j,jbase=11pt,magstyle=nomag*]{bxjsreport}
% \documentclass[uplatex, dvipdfmx, a4paper, 11ptj, report]{jsbook}
% small japanese font size:     9pt, 10pt, 11pt, 12pt, 14pt, ... (please refer the document of jsclasses)
% word-like japanese font size: 10ptj 10.5ptj, 11ptj, 12ptj (or jbase=xxpt (without 'j') if error is occured)

\input{preamble.tex}

\backmatter
\setchapterxr[thesis][bibliography]{1}


\begin{document}

% % bibtex
% \bibliographystyle{}
% \bibliography{}

% bibliography environment
\begin{thebibliography}{99}
% \markright{参考文献}
% \onehalfspacing

%1章
\bibitem{nishikawa_2018}
Yuri Nishikawa, Hitoshi Sato, and Jun Ozawa, ``Multiple sports player tracking system based on graph optimization using low-cost cameras'', 2018 IEEE International Conference on Consumer Electronics, pp.1--4, 2018.

\bibitem{nishikawa_2018_2}
西川由理, 佐藤仁, 小澤順,  ``グラフ最適化を用いた多人数追跡手法におけるグリッドマップ生成の並列化'', 人工知能学会全国大会論文集 2018年度人工知能学会全国大会（第32回）論文集, pp.2D101--2D101, 2018.

\bibitem{Teuliere_2011}
Teuliere C, Eck L, and Marchand E, ``Chasing a moving target from a flying uav'', Conference on Intelligent Robots and Systems (IROS), pp.4929--4934, 2011.

\bibitem{bethke_2007}
Bethke B, Valenti M, and How J, ``Cooperative vision based estimation and tracking using multiple UAVs'', Advances in cooperative control and optimization, pp.179--189, 2007.

\bibitem{nasser_2013}
T Nasser, J Sturm, and D Cremers, ``FollwMe: Person following and gesture recognition with a quadrocopter'', Proceedings in IEEE/RSJ IROS, pp.624--630, 2013.

\bibitem{price_2018}
E Price, G Lawless, H H Bulthoff, M Black, and A Ahmad, ``Deep Neural Network-based Cooperative Visual Tracking through Multiple Micro Aerial Vehicles'', arXiv preprint, arXiv:1820.01346, 2018.

\bibitem{wang_2009}
J Wang, W B Chen, and V Temu, ``Multi-Vehicle Motion Planning for Search and Tracking.'', IEEE Conference on Multimedia Information Processing and Retrieval (MIPR), pp.352--355, 2018.

\bibitem{bajracharya_2009}
M Bajracharya, B Moghaddam, A Howard, S Brennan, and L H Matthies, ``A Fast Stereo-Based System for Detecting and Tracking Pedestrians from a Moving Vehicle.'', The Int'l J. Robotics Research, Vol.28,pp.1466--1485, 2009.

\bibitem{furukawa_2006}
T Furukawa, F Bourgault, B Lavis, and H F Durrant-Whyte, ``Recursive Bayesian search-and-tracking using coordinated UAVs for lost targets.'', Proceedings of IEEE International Conference on Robotics and Automation, pp.2521--2526, 2006.

\bibitem{furukawa_2012}
T Furukawa, L C Mak, H Durrant-Whyte, and R Madhavan, ``Autonomous bayesian search and tracking. and its experimental validation.', Advanced Robotics, 26(5-6):pp.461--485, 2012.

\bibitem{pack_2009}
Pack D J, P Delima, and G J Toussaint, ``Cooperative control of UAVs for localization of intermittently emitting mobile targets'', IEEE Transactions on Systems,Man,and Cybernetics, vol.39,no.4,pp.959--970, 2009.
%ここまで1章




\end{thebibliography}


\end{document}
